Determining the alternatives for scalar implicature

### 2016-02-01 Paper/Paper.tex
tweaks in meeting

\begin{abstract}
Successful communication regularly requires listeners to make pragmatic
inferences - enrichments beyond the literal meaning of a speaker's
utterance. For example, when interpreting a sentence such as ``Alice ate
some of the cookies,'' listeners routinely infer that Alice did not eat
all of them. A Gricean account of this phenomena assumes the presence of
alternatives (like ``all of the cookies'') with varying degrees of
informativity, but it remains an open question precisely what these
alternatives are. We collect empirical measurements of speaker and
listener judgments and use these as inputs to a computational model of
pragmatic inference. This approach allows us to test hypotheses about
how well different sets of alternatives predict implicature performance
across a range of different scales. Our findings suggest that
comprehenders likely consider a much broader set of alternatives beyond
those entailed by the initial description.

@@

How much of what we mean comes from the words that go unsaid? As
listeners, our ability to make precise inferences about a speaker's
intended meaning in context is indispensable to successful
communication. For example, listeners commonly enrich the meaning of the
scalar item \emph{some} to \emph{some but not all} in sentences like
``Alice ate some of the cookies'' (Grice, 1975; Horn, 1984; Levinson,
2000). These inferences, called \emph{scalar implicatures}, have been an
important test case for understanding pragmatic inferences more
generally. A Gricean account of this phenomenon assumes listeners reason
about a speaker's intended meaning by incorporating knowledge about a)
alternative scalar items a speaker could have used (such as \emph{all})
and b) the relative informativity of using such alternatives (Grice,
1975). According to this account, a listener will infer that the speaker
must have intended that Alice did not eat all the cookies because it
would have been underinformative to use the descriptor \emph{some} when
the alternative \emph{all} could have been used just as easily.

But what are the alternatives that should be considered in the
implicature computation more generally? Under classic accounts,
listeners consider only those words whose meanings entail the actual
message (Horn, 1972), and these alternatives enter into conventionalized
or semi-conventionalized scales (Levinson, 2000). For example, because
\emph{all} entails \emph{some}, and hence is a ``stronger'' meaning,
\emph{all} should be considered as an alternative to \emph{some} in
implicatures. Similar scales exist for non-quantifier scales, e.g.
\emph{loved} entails \emph{liked} (and hence ``I liked the movie''
implicates I didn't love it).

Recent empirical evidence has called into question whether entailment
scales are all that is necessary for understanding scalar implicature.
For example, Degen \& Tanenhaus (2015) demonstrated that the scalar item
\emph{some} was judged less appropriate when exact numbers were seen as
viable alternatives. And in a different paradigm, Tiel (2014) found
converging evidence that \emph{some} was judged to be atypical for small
quantities. These data provide indirect evidence about a broader set of
alternatives: since \emph{some} is logically true of sets with one or
two members, these authors argued that the presence of salient
alternatives (the words \emph{one} and \emph{two}, for example) reduced
the felicity of \emph{some} via a pragmatic inference.

By formalizing pragmatic reasoning, computational models can help
provide more direct evidence about the role that alternatives play. The
``rational speech act'' model (RSA) is one recent framework for
understanding inferences about meaning in context (Frank \& Goodman,
2012; N. D. Goodman \& Stuhlmuller, 2013). RSA models frame language
understanding as a special case of social cognition, in which listeners
and speakers reason recursively about one another's goals. In the case
of scalar implicature, a listener makes a probabilistic inference about
what the speaker's most likely communicative goal was, given that she
picked the quantifier \emph{some} rather than the stronger quantifier
\emph{all}. In turn, the speaker reasons about what message would best
convey her intended meaning to the listener, given that he is reasoning
in this way. This recursion is grounded in a ``literal'' listener who
reasons only according to the basic truth-functional semantics of the
language.

Franke (2014) used an RSA-style model to assess what alternatives a
speaker would need to consider in order to produce the
typicality/felicity ratings reported by Degen \& Tanenhaus (2015) and
Tiel (2014) for the scale \emph{some}/\emph{all}. In order to do this,
Franke (2014)'s model assigned weights to a set of alternative numerical
expressions. Surprisingly, along with weighting \emph{one} highly (a
conclusion that was supported by the empirical work), the best-fitting
model assigned substantial weight to \emph{none} as an alternative to
\emph{some}. This finding was especially surprising considering the
emphasis of standard theories on scalar items that stand in entailment
relationships with one another (e.g. \emph{one} entails \emph{some} even
if it is not classically considered to be part of the scale).

In our current work, we pick up where these previous studies left off,
considering the set of alternatives for implicature using the RSA model.
To gain empirical traction on this issue, however, we broaden the set of
scales we consider. Our inspiration for this move comes from work by Van
Tiel, Van Miltenburg, Zevakhina, \& Geurts (2014), who examined a
phenomenon that they dubbed ``scalar diversity,'' namely the substantial
difference in the strength of scalar implicature across a variety of
scalar pairs (e.g. \emph{liked}/\emph{loved,} or
\emph{palatable}/\emph{delicious.}). Making use of some of this
diversity allows us to investigate the ways that different alternative
sets give rise to implicatures of different strengths across scales.

We begin by presenting the computational framework we use throughout the
paper. We next describe a series of experiments designed to measure both
the literal semantics of a set of scalar items and comprehenders'
pragmatic judgments for these same items. These experiments allow us to
compare the effects of different alternative sets on our ability to
model listeners' pragmatic judgments. To preview our results: we find
that standard entailment alternatives do not allow us to fit
participants' judgments, but that expanding the range of alternatives
empirically (by asking participants to generate alternative messages)
allows us to model listener judgments with high accuracy.

@@

We begin by giving a brief presentation of the basic RSA model. This
model simulates the judgments of a pragmatic listener who wants to infer
a speaker's intended meaning \(m\) from her utterance \(u\). For
simplicity, we present a version of this model in which there is only
full recursion: that is, the pragmatic listener reasons about a
pragmatic speaker, who in turn reasons about a ``literal listener.'' We
assume throughout that this computation takes place in a signaling game
(Lewis, 1969) with a fixed set of possible meanings \(m \in M\) and a
fixed possible set of utterances \(u \in U\), with both known to both
participants. Our goal in this study is to determine what utterances
fall in \(U\).

@@

\noindent In other words, the probability of a particular meaning given
an utterance is proportional to the speaker's probability of using that
particular utterance to express that meaning, weighted by a prior over
meanings. This prior represents the listener's \emph{a priori}
expectations about plausible meanings, independent of the utterance.
Because our experiments take place in a context in which listeners
should have very little expectation about which meanings speakers want
to convey, for simplicity we assume a uniform prior \(p(m) \propto 1\).

@@

\noindent where \(C(u)\) is the cost of a particular utterance,
\(-log(p_{L_0})\) represents the \emph{surprisal} of the message for the
literal listener (the information content of the utterance), and
\(\alpha\) is a parameter in a standard choice rule. If \(\alpha=0\),
speakers choose randomly and as \(\alpha \rightarrow \infty\), they
greedily choose the highest probability alternative. In our simulations
below, we treat \(\alpha\) as a free parameter and fit it to the data.

To instantiate our signaling game with a tractable message set \(M\), in
our studies we adopt the world of restaurant reviews as our
communication game. We assume that speakers and listeners are trying to
communicate the number of stars in an online restaurant review (where
\(m \in \{1, 2, 3, 4, 5\}\)). We then use experiments to measure three
components of the model. First, to measure literal semantics
\({p_{L_0} (m \mid u)}\) we ask experiment participants to judge whether
a message is compatible with a particular meaning (Experiment 1).
Second, to generate a set of plausible alternative messages in \(U\), we
elicit alternatives directly (Experiment 2). Lastly, to obtain human
\(L_1\) pragmatic judgments, we ask participants to interpret a
speaker's utterances (Experiment 3).

@@

\begin{CodeChunk}
\begin{figure}[t]
\includegraphics{figs/allScalesTable-1} \caption[Stimuli for Experiments 1, 2, and 3]{Stimuli for Experiments 1, 2, and 3}\label{fig:allScalesTable}
\end{figure}
\end{CodeChunk}

\begin{CodeChunk}
\begin{figure*}[t]

@@

\caption[(Left) A trial from Experiment 1 (literal listener) with the target scalar `liked]{(Left) A trial from Experiment 1 (literal listener) with the target scalar `liked.' (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar `liked.'}\label{fig:stimuli_exp1}
\end{figure*}
\end{CodeChunk}

Experiment 1 was conducted to approximate literal listener semantics -
\(p_{L_0}(m \mid u)\) in Equation (2), for five pairs of scalar items
taken from Tiel (2014). We include three conditions in Experiment 1,
corresponding to the sets of alternatives within a scale that
participants were presented with: two-alternatives (``entailment''),
four-alternatives, and five-alternatives. The two-alternatives condition
makes a test of the hypothesis that the two members of the classic Horn
(entailment) scale (Horn, 1972) are the only alternatives necessary to
predict the strength of listeners' pragmatic inference. The four and
five-alternatives conditions then add successively more alternatives to
test whether including a larger number of alternatives will increase
model
fit.\footnote{Note that alternatives in the four and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
A secondary goal of Experiment 1 is to test whether the set of
alternatives queried during literal semantic elicitation impacts literal
semantic judgments. If it does we should see differences in these
judgments for shared items between experiments.

@@

Conditions were run sequentially. In each condition we recruited 30
participants from Amazon Mechanical Turk (AMT). In the two-alternatives
condition (Experiment 1a), 16 participants were excluded for either
failing to pass two training trails or were not native English speakers,
leaving a total sample of 14
participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials. We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.}
In the four alternative condition (Experiment 1b), 7 participants were
excluded for either failing to pass two training trials or were not
native English speakers, leaving a total sample of 23 participants. In
the five alternative condition (Experiment 1c), 3 participants were
excluded for either failing to pass two training trials or were not
native English speakers, leaving a total sample of 27.

@@

The two-alternatives condition included only the scalar pairs from Tiel
(2014). The four-alternatives condition included the two scalar items
plus the top two alternatives generated for each scalar family by
participants in Experiment 2. The five-alternatives condition included
the four previous items plus one more neutral item chosen from
alternatives generated in Experiment 2. See Figure
\ref{fig:allScalesTable} for the complete list of alternatives used in
each condition.

@@

Figure \ref{fig:exp1Plots} plots literal listener \(p_{L0}(m|u)\) scalar
item distributions for the three conditions. Each row shows a unique
scalar family with items ordered horizontally by valence. Several trends
are visible. First, in each scale, the alternatives spanned the star
scale, such that there were scalar items that were highly compatible
with both the lowest and highest numbers of stars. Second, participant
compatibility judgments match intuitive literal semantics. That is, both
weaker (e.g. \emph{some} or \emph{good}) and stronger (e.g. \emph{all}
or \emph{excellent}) entailment items were seen as compatible with
five-star ratings. This means participants' compatibility judgements
reflect literal semantic intuitions, not enriched pragmatic judgments.
We see clear variability between scalar families (literal semantic
distributions for \emph{memorable} are considerably different from
\emph{palatable}), but also substantial consistency across conditions
(compatibility judgments for individual scalar items are consistent in
Experiments 1a,b,c).

@@

To examine the effect different alternative sets have on implicature, we
needed a way of expanding alternative sets beyond entailment pairs. We
addressed this issue by adopting a modified cloze task to elicit
alternatives empirically. This design was inspired by Experiment 3 of
Tiel (2014).

@@

\begin{CodeChunk}
\begin{figure}[t]

@@

Figure \ref{fig:exp2Plots} plots pragmatic listener judgment
distributions for ``weak'' / ``strong'' scalar pairs (e.g.
\emph{good}/\emph{excellent}). Several trends are visible. First, in
each scale participants generated implicatures. They were substantially
less likely to assign high star ratings to weaker scalar terms, despite
the literal semantic compatibility of those terms with those states
shown in Experiment 1. Second, the size of the difference between strong
and weak scalar items varied considerably across scales, consistent with
previous work (Tiel, 2014).

@@

@@

In our current work, we used the rational speech act framework to
investigate the set of alternatives that best allowed the model to
predict pragmatic judgments across a series of different scales. We
found that the best predictions came when a range of scale-dependent
negative and neutral alternatives were added to the implicature
computation, suggesting the importance of considering non-entailment
alternatives. This work builds on previous investigations, reinforcing
the claim that negative alternatives are critical for understanding
implicature (Franke, 2014), and replicates and extends findings that
different lexical scales produce strikingly different patterns of
inference (Tiel, 2014).

@@

Frank, M., \& Goodman, N. (2012). Predicting pragmatic reasoning in
language games. \emph{Science}, \emph{336}(6084), 998.

@@

Tiel, B. van. (2014). Quantity matters: Implicatures, typicality, and
truth.

Van Tiel, B., Van Miltenburg, E., Zevakhina, N., \& Geurts, B. (2014).
Scalar diversity. \emph{Journal of Semantics}, ffu017.

>>>>

\begin{abstract}
Successful communication regularly requires listeners to make pragmatic
inferences - enrichments beyond the literal meaning of a speaker's
utterance. For example, when interpreting a sentence such as ``Alice ate
some of the cookies,'' listeners routinely infer that Alice did not eat
all of them. A Gricean account of this phenomena assumes the presence of
alternatives (like ``all of the cookies'') with varying degrees of
informativity, but it remains an open question precisely what these
alternatives are. To address this question, we collect empirical
measurements of speaker and listener judgments about varying sets of
alternatives across a range of scales and use these as inputs to a
computational model of pragmatic inference. This approach allows us to
test hypotheses about how well different sets of alternatives predict
implicature performance. Our findings suggest that comprehenders likely
consider a broader set of alternatives beyond those logically entailed
by the initial message.

@@

How much of what we mean comes from the words that go unsaid? As
listeners, our ability to make precise inferences about a speaker's
intended meaning in context is indispensable to successful
communication. For example, listeners commonly enrich the meaning of the
scalar item \emph{some} to \emph{some but not all} in sentences like
``Alice ate some of the cookies'' (Grice, 1975; Horn, 1984; Levinson,
2000). These inferences, called \emph{scalar implicatures}, have been an
important test case for understanding pragmatic inferences more
generally. A Gricean account of this phenomenon assumes listeners reason
about a speaker's intended meaning by incorporating knowledge about A)
alternative scalar items a speaker could have used (such as \emph{all})
and B) the relative informativity of using such alternatives (Grice,
1975). According to this account, a listener will infer that the speaker
must have intended that Alice did not eat all the cookies because it
would have been underinformative to use the descriptor \emph{some} when
the alternative \emph{all} could have been used just as easily.

But what are the alternatives that should be considered in the
implicature computation more generally? Under classic accounts,
listeners consider only those words whose meanings entail the actual
message (Horn, 1972), and these alternatives enter into conventionalized
or semi-conventionalized scales (Levinson, 2000). For example, because
\emph{all} entails \emph{some}, and hence is a ``stronger'' meaning,
\emph{all} should be considered as an alternative to \emph{some} in
implicatures. Similar scales exist for non-quantifier scales, e.g.
\emph{loved} entails \emph{liked} (and hence ``I liked the movie''
implicates that I didn't love it).

Recent empirical evidence has called into question whether entailment
scales are all that is necessary for understanding scalar implicature.
For example, Degen \& Tanenhaus (2015) demonstrated that the scalar item
\emph{some} was judged less appropriate when exact numbers were seen as
viable alternatives. And in a different paradigm, {van Tiel} (2014)
found converging evidence that \emph{some} was judged to be atypical for
small quantities. These data provide indirect evidence about a broader
set of alternatives. Since \emph{some} is logically true of sets with
one or two members, these authors argued that the presence of salient
alternatives (the words \emph{one} and \emph{two}, for example) reduced
the felicity of \emph{some} via a pragmatic inference.

By formalizing pragmatic reasoning, computational models can help
provide more direct evidence about the role that alternatives play. The
``rational speech act'' model (RSA) is one recent framework for
understanding inferences about meaning in context (Frank \& Goodman,
2012; Goodman \& Stuhlmuller, 2013). RSA models frame language
understanding as a special case of social cognition, in which listeners
and speakers reason recursively about one another's goals. In the case
of scalar implicature, a listener makes a probabilistic inference about
what the speaker's most likely communicative goal was, given that she
picked the quantifier \emph{some} rather than the stronger quantifier
\emph{all}. In turn, the speaker reasons about what message would best
convey her intended meaning to the listener, given that he is reasoning
in this way. This recursion is grounded in a ``literal'' listener who
reasons only according to the basic truth-functional semantics of the
language.

Franke (2014) used an RSA-style model to assess what alternatives a
speaker would need to consider in order to produce the
typicality/felicity ratings reported by Degen \& Tanenhaus (2015) and
{van Tiel} (2014) for the scale \emph{some}/\emph{all}. In order to do
this, Franke (2014)'s model assigned weights to a set of alternative
numerical expressions. Surprisingly, along with weighting \emph{one}
highly (a conclusion that was supported by the empirical work), the
best-fitting model assigned substantial weight to \emph{none} as an
alternative to \emph{some}. This finding was especially surprising
considering the emphasis of standard theories on scalar items that stand
in entailment relationships with one another (e.g. \emph{one} entails
\emph{some} even if it is not classically considered to be part of the
scale).

In our current work, we pick up where these previous studies left off,
considering the set of alternatives for implicature using the RSA model.
To gain empirical traction on this issue, however, we broaden the set of
scales we consider. Our inspiration for this move comes from work by
{van Tiel}, Van Miltenburg, Zevakhina, \& Geurts (2014), who examined a
phenomenon that they dubbed ``scalar diversity,'' namely the substantial
difference in the strength of scalar implicature across a variety of
scalar pairs (e.g., \emph{liked} / \emph{loved,} \emph{palatable} /
\emph{delicious}). Making use of this diversity allows us to investigate
the ways that different alternative sets give rise to implicatures of
different strengths across scales.

We begin by presenting the computational framework we use throughout the
paper. We next describe a series of experiments designed to measure both
the literal semantics of a set of scalar items and comprehenders'
pragmatic judgments for these same items. These experiments allow us to
compare the effects of different alternative sets on our ability to
model listeners' pragmatic judgments. To preview our results: we find
that standard entailment alternatives do not allow us to fit
participants' judgments, but that expanding the range of alternatives
empirically (by asking participants to generate alternative messages)
allows us to predict listeners' pragmatic judgments with high accuracy.

@@

We begin by giving a brief presentation of the basic RSA model. This
model simulates the judgments of a pragmatic listener who wants to infer
a speaker's intended meaning \(m\) from her utterance \(u\). For
simplicity, we present a version of this model in which there is only
one full recursion: The pragmatic listener reasons about a pragmatic
speaker, who in turn reasons about a ``literal listener.'' We assume
throughout that this computation takes place in a signaling game (Lewis,
1969) with a fixed set of possible meanings \(m \in M\) and a fixed
possible set of utterances \(u \in U\), with both known to both
participants. Our goal in this study is to determine which utterances
fall in \(U\).

@@

\noindent In other words, the probability of a particular meaning given
an utterance is proportional to the speaker's probability of using that
particular utterance to express that meaning, weighted by a prior over
meanings. This prior represents the listener's \emph{a priori}
expectations about plausible meanings, independent of the utterance.
Because our experiments take place in a context in which listeners
should have very little expectation about which meanings speakers want
to convey, for simplicity we assume a uniform prior where
\(p(m) \propto 1\).

@@

\noindent where \(C(u)\) is the cost of a particular utterance,
\(-log(p_{L_0})\) represents the \emph{surprisal} of the message for the
literal listener (the information content of the utterance), and
\(\alpha\) is a parameter in a standard choice rule. If \(\alpha=0\),
speakers choose randomly; as \(\alpha \rightarrow \infty\), they
greedily choose the highest probability alternative. In our simulations
below, we treat \(\alpha\) as a free parameter and fit it to the data.

To instantiate our signaling game with a tractable message set \(M\), in
our studies we adopt the world of restaurant reviews as our
communication game. We assume that speakers and listeners are trying to
communicate the number of stars in an online restaurant review (where
\(m \in \{1...5\}\)). We then use experiments to measure three
components of the model. First, to measure literal semantics
\({p_{L_0} (m \mid u)}\) we ask experiment participants to judge whether
a message is compatible with a particular meaning (Experiment 1).
Second, to generate a set of plausible alternative messages in \(U\), we
elicit alternatives directly (Experiment 2). Lastly, to obtain human
\(L_1\) pragmatic judgments, we ask participants to interpret a
speaker's utterances (Experiment 3).

@@

\begin{CodeChunk}
\begin{figure}[t]
\includegraphics{figs/allScalesTable-1} \caption[Alternative sets for Experiments 1, 2, and 3]{Alternative sets for Experiments 1, 2, and 3.}\label{fig:allScalesTable}
\end{figure}
\end{CodeChunk}

\begin{CodeChunk}
\captionsetup{width=0.8\textwidth}\begin{figure*}[t]

@@

\caption[(Left) A trial from Experiment 1 (literal listener) with the target scalar "liked]{(Left) A trial from Experiment 1 (literal listener) with the target scalar "liked."(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar "liked."}\label{fig:stimuli_exp1}
\end{figure*}
\end{CodeChunk}

Experiment 1 was conducted to approximate literal listener
semantics---\(p_{L_0}(m \mid u)\) in Equation (2)---for five pairs of
scalar items taken from {van Tiel} (2014). We include three conditions
in Experiment 1, corresponding to the sets of alternatives within a
scale that participants were presented with: two-alternatives
(``entailment''), four-alternatives, and five-alternatives. The
two-alternatives condition makes a test of the hypothesis that the two
members of the classic Horn (entailment) scale (Horn, 1972) are the only
alternatives necessary to predict the strength of listeners' pragmatic
inference. The four and five-alternatives conditions then add
successively more alternatives to test whether including a larger number
of alternatives will increase model
fit.\footnote{Note that alternatives in the four and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
A secondary goal of Experiment 1 is to test whether the set of
alternatives queried during literal semantic elicitation impacts literal
semantic judgments. If it does we should see differences in these
judgments for shared items between experiments.

@@

Conditions were run sequentially. In each condition we recruited 30
participants from Amazon Mechanical Turk (AMT). In the two-alternatives
condition (Experiment 1a), 16 participants were excluded for either
failing to pass two training trails or because they were not native
English speakers, leaving a total sample of 14
participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials. We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.}
In the four alternative condition (Experiment 1b), 7 participants were
excluded for either failing to pass two training trials or not being
native English speakers, leaving a total sample of 23 participants. In
the five alternative condition (Experiment 1c), 3 participants were
excluded for either failing to pass two training trials or not being
native English speakers, leaving a total sample of 27.

@@

The two-alternatives condition included only the two terms in the pairs
from van Tiel (2014). The four-alternatives condition included the two
scalar items plus the top two alternatives generated for each scalar
family by participants in Experiment 2. The five-alternatives condition
included the four previous items plus one more neutral item chosen from
alternatives generated in Experiment 2. See Figure
\ref{fig:allScalesTable} for the complete list of alternatives used in
each condition.

@@

Figure \ref{fig:exp1Plots} plots the estimated literal listener
semantics for the three conditions. Each row shows a unique scalar
family with items ordered horizontally by valence. Several trends are
visible. First, in each scale, the alternatives spanned the star scale,
such that there were scalar items that were highly compatible with both
the lowest and highest numbers of stars. Second, participant
compatibility judgments match intuitive literal semantics. That is, both
weaker (e.g. \emph{some} or \emph{good}) and stronger (e.g. \emph{all}
or \emph{excellent}) entailment items were seen as compatible with
five-star ratings. This means participants' compatibility judgements
reflect literal semantic intuitions, not enriched pragmatic judgments.
We see clear variability between scalar families (literal semantic
distributions for \emph{memorable} are considerably different from
\emph{palatable}), but also substantial consistency across conditions
(compatibility judgments for individual scalar items are consistent in
Experiments 1a,b,c).

@@

To examine the effect different alternative sets have on implicature, we
needed a way of expanding alternative sets beyond entailment pairs. We
addressed this issue by adopting a modified cloze task to elicit
alternatives empirically. This design was inspired by Experiment 3 of
{van Tiel} (2014).

@@

\begin{CodeChunk}
\captionsetup{width=0.8\textwidth}\begin{figure}[t]

@@

Figure \ref{fig:exp2Plots} plots pragmatic listener judgment
distributions for ``weak'' / ``strong'' scalar pairs (e.g.
\emph{good}/\emph{excellent}). Several trends are visible. First, in
each scale participants generated implicatures. They were substantially
less likely to assign high star ratings to weaker scalar terms, despite
the literal semantic compatibility of those terms with those states
shown in Experiment 1. Second, the size of the difference between strong
and weak scalar items varied considerably across scales, consistent with
previous work ({van Tiel}, 2014).

@@

\captionsetup{width=0.8\textwidth}

@@

In our current work, we used the rational speech act framework to
investigate the set of alternatives that best allowed the model to
predict pragmatic judgments across a series of different scales. We
found that the best predictions came when a range of scale-dependent
negative and neutral alternatives were added to the implicature
computation, suggesting the importance of considering non-entailment
alternatives. This work builds on previous investigations, reinforcing
the claim that negative alternatives are critical for understanding
implicature (Franke, 2014), and replicates and extends findings that
different lexical scales produce strikingly different patterns of
inference ({van Tiel}, 2014).

@@

Frank, M., \& Goodman, N. D. (2012). Predicting pragmatic reasoning in
language games. \emph{Science}, \emph{336}(6084), 998.

@@

{van Tiel}, B. J. M. (2014). Quantity matters: Implicatures, typicality,
and truth.

{van Tiel}, B. J. M., Van Miltenburg, E., Zevakhina, N., \& Geurts, B.
(2014). Scalar diversity. \emph{Journal of Semantics}, ffu017.
